Long-form recording of infant body position in the home using wearable inertial sensors

### 2023-03-16 manuscript.Rmd
get new research possibilities going

Beyond group and individual models, there were many degrees of freedom in our choice of how best to model body position. For the sake of brevity, we did not report every possible variation, only the best approach. However, our openly shared data mean that researchers can experiment with different sets of motion features, different sets of training data, different machine learning algorithms, and different sets of hyperparameters. As in past work [@AiraksinenRasanen2020], performance is best when using all four sensors and degrades when using any subset of two (i.e., hips only, left leg only). We tested but did not report models that used either only accelerometer data and only gyroscope data; in both cases, performance is degraded compared with models that use both types of motion. We also tried different machine learning algorithms (XGBoost, Tabnet), but found that random forest models performed the best. Finally, we tried modeling each age group separately, but found no boost in performance by tailoring to the particular age group.
<!-- DATA CITE -->

## What does this get us?

Other things look a bit wacky, but within-day heterogeniety is the point. Shouldn't be surprised to find it. Some can confirm on video. Activity are a big shaper of behavior, have enough behavior to actually see it.

See how other aspects of behavior align w/ movement in real time. See how new motor skills relate to chg in daily behavior. 
LINK TO AGE DIFFS. Some outlier-ish data in age comparisons, but nothing out of the ordinary (hard to know if it's the model or the behavior)

>>>>

Beyond group and individual models, there were many degrees of freedom in our choice of how best to model body position. For the sake of brevity, we did not report every possible variation, only the best approach. However, our openly shared data mean that researchers can experiment with different sets of motion features, different sets of training data, different machine learning algorithms, and different sets of hyperparameters. As in past work [@AiraksinenRasanen2020], performance is best when using all four sensors and degrades when using any subset of two (i.e., hips only, left leg only). We tested but did not report models that used either only accelerometer data and only gyroscope data; in both cases, performance is degraded compared with models that use both types of motion. We also tried different machine learning algorithms (XGBoost, Tabnet), but found that random forest models performed the best. Finally, we tried modeling each age group separately, but found no benefit to performance by tailoring to the particular age group.
<!-- DATA CITE -->

## Novel Research Possibilities

Long-form recordings of motor behavior bring about new research possibilities. Although past work using video [@Karasik2011; @ChenSchneider2022; @HerzbergFletcher2021] produced real-time data, such data were limited to a relatively small part of the infants' day. And although survey methods [@Survey] could capture moments scattered throughout the day, they do not produce real-time data. The combination of real-time, full-day data about infant motor behavior is unprecedented and offers new opportunities for understanding infants' everyday experiences. Collecting dense data over the entire variety of daily experiences helps to more accurately measure infants' experiences in aggregate (as in Figure \@ref(fig:age)) without biasing results from a particular type of activity (e.g., play). But as Figure \@ref(fig:timelines) shows, aggregating responses masks the rich information that is available from the entire individual timelines provided by long-form recordings.

In the past decade, developmental scientists have discovered that the distributional structure of infants' experiences matter for learning [@ClerkinHart2017; @KachergisYu2017; @RazAbney2019].

Other things look a bit wacky, but within-day heterogeniety is the point. Shouldn't be surprised to find it. Some can confirm on video. Activity are a big shaper of behavior, have enough behavior to actually see it. 
LINK TO AGE DIFFS. Some outlier-ish data in age comparisons, but nothing out of the ordinary (hard to know if it's the model or the behavior)

See how other aspects of behavior align w/ movement in real time. See how new motor skills relate to chg in daily behavior.
